Chlorophylla

### 2019-02-28 Chlorophyll_a .Rmd
....

# Pixels and matching
match_index <- knnx.index(data = as.matrix(daily_chloro_data[,1:2]),
                          query = as.matrix(combined_US[,5:6]), k = 1)

# # # Select SST pixels nearest to insitu sites
pixel_match <- daily_chloro_data[match_index,] %>%
  unite(col = combi, lon, lat, sep = "/", remove = F) %>%
  mutate(site = combined_US$site)

>>>>

unique_pixel <- MODIS_Chloro %>%
  select(lon, lat) %>%
  unique()

daily_chloro_data <- MODIS_Chloro %>%
  dplyr::mutate(date = as.Date(date)) %>% 
  mutate(month = month(date),
         day = day(date),
         year = year(date)) %>% 
  dplyr::group_by(lon, lat, day, month, year) %>% 
  dplyr::summarise(chloro = mean(chloro, na.rm = TRUE))

match_index <- knnx.index(data = as.matrix(daily_chloro_data[,1:2]),
                          query = as.matrix(combined_US[,5:6]), k = 1)

pixel_match <- daily_chloro_data[match_index,] %>%
  unite(col = combi, lon, lat, sep = "/", remove = F) %>%
  mutate(site = combined_US$site)
